---
title: "Heartrate"
author: "Julian During"
date: "27 12 2020"
output: 
  html_document: 
    theme: cosmo
    toc: yes
    number_sections: yes
    code_folding: hide
params:
  rerun: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("libraries.R")
theme_set(theme_light())

dir_ls("R") %>% 
  walk(
    ~ knitr::read_chunk(
      path = .x,
      labels = path_ext_remove(path_file(.x))))
```

```{r, eval=!params$rerun, include=FALSE}
loadd(glm_net_workflow)
loadd(gg_eda_act_ride)
loadd(gg_glm_net_fit)
loadd(gg_eda_act_run)
loadd(gg_glm_net_vip)
loadd(glm_net_tune)
loadd(rf_workflow)
loadd(glm_net_fit)
loadd(df_act_raw)
loadd(gg_rf_fit)
loadd(gg_rf_vip)
loadd(rf_tune)
loadd(rf_fit)
loadd(df_act)
```


# Idea

In this post, I want to explore the heart rate data of my Strava Activities.

Heart rate can be considered as a measurement of the intensity of an physical
activity.
So in this post, I want to find out, what are the driving forces behind the
intensity level of my activities. 
For future activities I would like to be able to determine, if the activity was
less or more exhausting than comparable activities.

In this post, the following libraries are used:

# Data

All my Strava activities are stored in a private Github repository. How this
can be done, is described in an earlier post.

## Activities with Heartrate

Load all activities from the repository. Filter for those with heart rate data:

```{r act_raw}
```

```{r, eval=params$rerun}
df_act_raw <- act_raw()
```

The raw data consists of `r nrow(df_act_raw)` activities. The aim of this post
is to predict the `average_heartrate` with the available information.

```{r, echo=FALSE}
df_act_raw
```

Preprocess data. Only select relevant columns and convert the `start_date` from
a timestamp to a date column.

```{r pre_process_act}
```

```{r, eval=params$rerun}
df_act <- pre_process_act(df_act_raw)
```

```{r, echo=FALSE}
df_act
```


## EDA Plots Activities {.tabset}

### Runs

```{r vis_eda_act_run}
```

```{r, echo=FALSE}
gg_eda_act_run
```

### Rides

```{r vis_eda_act_ride}
```

```{r, echo=FALSE}
gg_eda_act_ride
```

# Modeling {.tabset}

Set initial splits:

```{r eval=FALSE}
set.seed(123)
init_split <- initial_split(df_act, strata = average_heartrate)
bpm_train <- training(init_split)
bpm_test <- testing(init_split)
set.seed(234)
bpm_folds <- bootstraps(bpm_train, strata = average_heartrate)
```

## GLMNet

Define the workflow:

```{r glm_net_wf}
```

```{r}
glm_net_workflow
```

Tune the workflow:

```{r glm_net_tune_wf}
```

```{r include=FALSE}
glm_net_tune
```

```{r, echo=FALSE}
glm_net_tune
```

Determine the best parameter set:

```{r}
show_best(glm_net_tune, metric = "rmse")
```


Fit the model one last time with the determined parameters:

```{r glm_net_last_fit}
```

Evaluate the performance:

```{r include=FALSE}
glm_net_fit
```

```{r}
collect_metrics(glm_net_fit)
```

```{r}
gg_glm_net_fit
```

## Random Forest

Define the workflow:

```{r rf_wf}
```

```{r}
rf_workflow
```

Tune the workflow:

```{r rf_tune_wf}
```

```{r include=FALSE}
rf_tune
```

```{r, echo=FALSE}
rf_tune
```

Determine the best parameter set:

```{r}
show_best(rf_tune, metric = "rmse")
```


Fit the model one last time with the determined parameters:

```{r rf_last_fit}
```

Evaluate the performance:

```{r include=FALSE}
rf_fit
```

```{r}
collect_metrics(rf_fit)
```

```{r}
gg_rf_fit
```

# Variable Importance {.tabset}

```{r vis_vip}
```

## GLMNet

```{r, echo=FALSE}
gg_glm_net_vip
```

## Random Forest

```{r, echo=FALSE}
gg_rf_vip
```

# Save Model

```{r}
board_register_github(repo = "duju211/strava_act", branch = "master")

pin(rf_fit$.workflow[[1]], "rf_mod", board = "github")

board_disconnect("github")
```

